TrenchR: an R package for transparent microclimate and biophysical ecology

### 2022-07-28 ManuscriptTe.Rmd
minor updates

---
title: "Appendix S1"
author: "Buckley et al."
output:
  html_document: default
  word_document: default
  pdf_document: 
    pandoc_args: --listings
    includes:
      in_header: preamble.tex
---

>>>>

---
title: "Appendix S1"
author: "Buckley et al."
output:
  word_document: default
  html_document: default
  pdf_document: 
    pandoc_args: --listings
    includes:
      in_header: preamble.tex
---

### 2022-07-28 Manuscript_full.Rmd
Update link
minor updates

---
title: 'TrenchR: an R package for transparent microclimate and biophysical ecology'
author: 
  - "Lauren B. Buckley, Bryan A. Briones Ortiz, Isaac Caruso, Aji John, Ofir Levy,"
  - "Abigail V. Meyer, Eric A. Riddell, Yutaro Sakairi, and Juniper Simonis"
output:
  html_document: default
  word_document: default
  pdf_document: 
    pandoc_args: --listings
    includes:
      in_header: preamble.tex
bibliography: bibliography.bib
csl: methods-in-ecology-and-evolution.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

The TrenchR package (<http://trenchproject.github.io/TrenchR/>) aims to promote transparency and reproducibility. 
We welcome contributions and corrections from users. 
Our package was built using the devtools methodology (<https://github.com/r-lib/devtools>) with version control managed in Github. 
Issues and feature requests can be contributed in Github (<https://github.com/trenchproject/TrenchR>). 
The package is available via Github and has been submitted to CRAN.

@@

**Utility functions** calculate environmental metrics that form the basis of microclimate and biophysical models (e.g., zenith and declination angles, which describe the angles of incident sunlight), facilitate modeling diurnal temperature variation, and estimate biologically relevant aggregate metrics such as degree days available for oranismal development.

@@

## Data Availability

All code and data are available at <https://github.com/trenchproject/TrenchR>.

>>>>

---
title: 'TrenchR: an R package for transparent microclimate and biophysical ecology'
author: 
  - "Lauren B. Buckley, Bryan A. Briones Ortiz, Isaac Caruso, Aji John, Ofir Levy,"
  - "Abigail V. Meyer, Eric A. Riddell, Yutaro Sakairi, and Juniper Simonis"
output:
  word_document: default
  html_document: default
  pdf_document: 
    pandoc_args: --listings
    includes:
      in_header: preamble.tex
bibliography: bibliography.bib
csl: methods-in-ecology-and-evolution.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

The TrenchR package (<http://trenchproject.github.io/TrenchR/>) aims to promote transparency and reproducibility. 
We welcome contributions and corrections from users. 
Our package was built using the devtools methodology (<https://github.com/r-lib/devtools>) with version control managed in Github. 
Issues and feature requests can be contributed in Github (<https://github.com/trenchproject/TrenchR>). 
The package is available via CRAN and Github.

@@

**Utility functions** calculate environmental metrics that form the basis of microclimate and biophysical models (e.g., zenith and declination angles, which describe the angles of incident sunlight), facilitate modeling diurnal temperature variation, and estimate biologically relevant aggregate metrics such as degree days available for organismal development.

@@

## Data Availability
TrenchR is available at CRAN and <https://github.com/trenchproject/TrenchR>. All text, code, and data for this manuscript are available at <https://github.com/trenchproject/TrenchRmanuscript/>.
